BPMN Analyzer 2.0: Instantaneous, Comprehensible, and Fixable Control Flow Analysis for Realistic BPMN Models

### 2024-07-05 main.tex
Enlarge figures

\title{BPMN Analyzer 2.0: Instantaneous, Comprehensible, and Fixable Control Flow Analysis for BPMN Models}
% TODO: Update the DOI link to fit the extended version on arxiv

@@

% Solution
In this paper, we describe a new tool, the \textit{BPMN Analyzer 2.0}\footnote{
In the following, we will use BPMN Analyzer to refer to the BPMN Analyzer 2.0, not our previous BPMN Analyzer described in~\cite{krauterHigherorderTransformationApproach2024}.}, for analyzing BPMN process models to detect control flow errors \textit{already} during modeling. % TODO: Maybe give concrete examples of what we can check!
\autoref{fig:overview} shows an overview of the tool.
The tool front-end is based on the popular \textit{bpmn.io} ecosystem, while the analysis is implemented in Rust for performance and memory efficiency reasons.
The BPMN Analyzer is open-source and accessible online\footnote{\url{https://timkraeuter.com/bpmn-analyzer-js/}} alongside a video demonstration\footnote{\url{https://www.youtube.com/watch?v=MxXbNUl6IjE}}~\cite{krauterInstantaneousComprehensibleFixable2024}.

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width=1\linewidth]{images/counter-example}
	\caption{Interactive \textit{erroneous execution} shown in the BPMN Analyzer}
	\label{fig:counterexample}
\end{figure}

@@

\begin{figure}[ht]
	\centering
	\includegraphics[width=1\linewidth]{images/quick-fix}
	\caption{\textit{Quick fixes} in the analysis tool}
	\label{fig:quick-fixes}
\end{figure}

>>>>

\title{BPMN Analyzer 2.0: Instantaneous, Comprehensible, and Fixable Control Flow Analysis for Realistic BPMN Models}
% TODO: Update the DOI link to fit the extended version on arxiv

@@

% Solution
In this paper, we describe a new tool, the \textit{BPMN Analyzer 2.0}\footnote{
In the following, we will use BPMN Analyzer to refer to the BPMN Analyzer 2.0, not our previous work in~\cite{krauterHigherorderTransformationApproach2024}.}, for analyzing BPMN process models to detect control flow errors \textit{already} during modeling. % TODO: Maybe give concrete examples of what we can check!
\autoref{fig:overview} shows an overview of the tool.
The tool front-end is based on the popular \textit{bpmn.io} ecosystem, while the analysis is implemented in Rust for performance and memory efficiency reasons.
The BPMN Analyzer is open-source and accessible online\footnote{\url{https://timkraeuter.com/bpmn-analyzer-js/}} alongside a video demonstration\footnote{\url{https://www.youtube.com/watch?v=MxXbNUl6IjE}}~\cite{krauterInstantaneousComprehensibleFixable2024}.

@@

\begin{figure*}[ht]
	\centering
	\includegraphics[width=0.8\linewidth]{images/counter-example}
	\caption{\textit{Interactive} erroneous execution example shown in the BPMN Analyzer}
	\label{fig:counterexample}
\end{figure*}

@@

\begin{figure*}[ht]
	\centering
	\includegraphics[width=0.8\linewidth]{images/quick-fix}
	\caption{Suggested \textit{quick fixes} in the BPMN Analyzer}
	\label{fig:quick-fixes}
\end{figure*}
